Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-04-16 FIE2019.tex
Made anonymous
E-mailed version, also thanks to accreditors
A few bug fixes and ``Security by Implementation'' added on page 1.

% JHD to
% a) Add the Bonn work
% b) Add ABET stuff (done) and ask Tom P to cross-check.
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

% \author{\IEEEauthorblockN{Tom Crick}
% \IEEEauthorblockA{\textit{School of Education} \\
% \textit{Swansea University}\\
% Swansea, UK \\
% thomas.crick@swansea.ac.uk}
% \and
% \IEEEauthorblockN{James H. Davenport}
% \IEEEauthorblockA{\textit{Department of Computer Science} \\
% \textit{University of Bath}\\
% Bath, UK \\
% j.h.davenport@bath.ac.uk}
% \and
% \IEEEauthorblockN{Alastair Irons}
% \IEEEauthorblockA{\textit{Faculty of Technology} \\
% \textit{name of organization (of Aff.)}\\
% Sunderland University, Sunderland, UK\\
% alastair.irons@sunderland.ac.uk}
% \and
% \IEEEauthorblockN{Tom Prickett}
% \IEEEauthorblockA{\textit{Department of Computing and Information Sciences} \\
% \textit{name of organization (of Aff.)}\\
% Northumbria University, Newcastle upon Tyne, UK \\
% tom.prickett@northumbria.ac.uk}
% }

% compact IEEE author format for more than three authors...
\author{\IEEEauthorblockN{Tom Crick\IEEEauthorrefmark{1}, James
    H. Davenport\IEEEauthorrefmark{2}, Alastair
    Irons\IEEEauthorrefmark{3} and Tom Prickett\IEEEauthorrefmark{4}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Education, 
Swansea University, Swansea, UK; Email: thomas.crick@swansea.ac.uk} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}Dept.~Computer Science, 
University of Bath, Bath, UK; Email: j.h.davenport@bath.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Faculty of Technology, 
Sunderland University, Sunderland, UK; Email: alastair.irons@sunderland.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Dept.~Computer\&Information Sciences, 
Northumbria University, Newcastle upon Tyne, UK; Email: tom.prickett@northumbria.ac.uk}}

\maketitle

@@

In particular the expectation of ''Privacy by Design'' and and by "Privacy by Default" has significant implications for all software development with a European context that processes personal data. Whilst both ''Privacy by Design'' and ''Privacy by Default' have been expected good practices for a number of years, these expectations now have a legal dimension, at least in Europe. A number of studies have documented the challenges of aligning security methods in Agile Practices \cite{vanderHeijden:2018:EPS:3239235.3267426}. This further emphasizes the need for mainstream software developers and by extension Computer Science graduates to be versed in relevant security practices.

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager, BCS--The
Chartered Institute for IT for supplying the summary information
related to Accreditation.

>>>>

\newif\ifanon
\anontrue
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

% \author{\IEEEauthorblockN{Tom Crick}
% \IEEEauthorblockA{\textit{School of Education} \\
% \textit{Swansea University}\\
% Swansea, UK \\
% thomas.crick@swansea.ac.uk}
% \and
% \IEEEauthorblockN{James H. Davenport}
% \IEEEauthorblockA{\textit{Department of Computer Science} \\
% \textit{University of Bath}\\
% Bath, UK \\
% j.h.davenport@bath.ac.uk}
% \and
% \IEEEauthorblockN{Alastair Irons}
% \IEEEauthorblockA{\textit{Faculty of Technology} \\
% \textit{name of organization (of Aff.)}\\
% Sunderland University, Sunderland, UK\\
% alastair.irons@sunderland.ac.uk}
% \and
% \IEEEauthorblockN{Tom Prickett}
% \IEEEauthorblockA{\textit{Department of Computing and Information Sciences} \\
% \textit{name of organization (of Aff.)}\\
% Northumbria University, Newcastle upon Tyne, UK \\
% tom.prickett@northumbria.ac.uk}
% }
\ifanon
\author{Anonymous}
\else
% compact IEEE author format for more than three authors...
\author{\IEEEauthorblockN{Tom Crick\IEEEauthorrefmark{1}, James
    H. Davenport\IEEEauthorrefmark{2}, Alastair
    Irons\IEEEauthorrefmark{3} and Tom Prickett\IEEEauthorrefmark{4}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Education, 
Swansea University, Swansea, UK; Email: thomas.crick@swansea.ac.uk} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}Dept.~Computer Science, 
University of Bath, Bath, UK; Email: j.h.davenport@bath.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Faculty of Technology, 
Sunderland University, Sunderland, UK; Email: alastair.irons@sunderland.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Dept.~Computer\&Information Sciences, 
Northumbria University, Newcastle upon Tyne, UK; Email: tom.prickett@northumbria.ac.uk}}
\fi
\maketitle

@@

In particular the expectation of ``Privacy by Design'' and and by ``Privacy by Default'' has significant implications for all software development with a European context that processes personal data. Whilst both ``Privacy by Design'' and ``Privacy by Default'' have been expected good practices for a number of years, these expectations now have a legal dimension, at least in Europe.

However, ``Privacy by Design'' is no good without ``Security by Implementation'', and many security weaknesses are implementation weaknesses.
A number of studies have documented the challenges of aligning security methods in Agile Practices \cite{vanderHeijden:2018:EPS:3239235.3267426}. This further emphasizes the need for mainstream software developers and by extension Computer Science graduates to be versed in relevant security practices.

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager, BCS--The
Chartered Institute for IT for supplying the summary information
related to Accreditation. Many people, accreditors and accredited, contributed to  improving the standard of Cybersecurity teaching, and spreading good practice.
